Correlation of filter methods

### 2019-07-01 analysis/eda.Rmd
update reports

source(here::here("code/99-packages.R"))
sourceDirectory("R")

# load drake objects
loadd(
  vi_data, nri_data, bands_data, coords_vi_nri_clean,

@@

  fv_nri_info.gain5, fv_nri_info.gain10,
  fv_nri_info.gain15, fv_nri_info.gain20,
  fv_nri_info.gain25, fv_nri_info.gain30
)
library("DataExplorer")
library("dplyr")
library("ggsci")
library("ggplot2")
library("rgdal")
```

>>>>

R.utils::sourceDirectory("R")

# load drake objects
drake::loadd(
  vi_data, nri_data, bands_data, coords_vi_nri_clean,

@@

  fv_nri_info.gain5, fv_nri_info.gain10,
  fv_nri_info.gain15, fv_nri_info.gain20,
  fv_nri_info.gain25, fv_nri_info.gain30
)
library("DataExplorer")
library("dplyr")
library("ggsci")
library("ggpubr")
library("ggplot2")
library("knitr")
```

### 2019-07-01 analysis/filter-correlation.Rmd
update reports

```{r filter-correlation-nri, dev = c("png", "pdf"), warning=FALSE}
# combine filter values

@@

```{r filter-correlation-5, echo = FALSE}
# file_move("docs/figure/filter-correlation.Rmd/correlation-nbins-1.pdf",
#           "code/98-paper/journal/")
# file_move("docs/figure/filter-correlation.Rmd/correlation-filter-nri-1.pdf",
#           "code/98-paper/journal/")
```

>>>>

```{r correlation-filter-nri, dev = c("png", "pdf"), warning=FALSE}
# combine filter values

@@

```{r filter-correlation-5, echo = FALSE}
system("sleep 5")
# file_move("docs/figure/filter-correlation.Rmd/correlation-nbins-1.pdf",
#           "code/98-paper/journal/")
# file_move("docs/figure/filter-correlation.Rmd/correlation-filter-nri-1.pdf",
#           "code/98-paper/journal/")
```
